Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-12-17 Manuscript/manuscript.tex
Small improvements in Introduction

Lipids with negatively charged headgroups, like phophatidylserine
play important role in biomembranes. Signaling domains interact with
anionic lipid membranes due to electrostatic and specific interactions
with negatively charged lipids \cite{lemmon08,leventis10}.
Anionic lipids and their interactions with ions play also role in membrane
fusion \cite{??}. \todo{Pavel can probably improve this and give a citation}
These interactions depend on
chemical details of lipid headgroups and binding of counter and co-ions
to anionic membranes.

Various interaction schemes have been proposed for the negatively charged
lipids with ions and other lipids. Some studies suggest that the
binding constant to negatively charged lipids is similar to zwitterionic
and the binding affinity is increased only due to the increased cation
concentration in the vicinity of the membrane \cite{seelig90,sinn06}.
On the other hand, calcium forms dehydrated complexes with PS headgroups
which cause phase separation \cite{hauser77,kurland79,hauser85,feigenson86,mattai89,roux90,roux91,boettcher11}.
Different theories are difficult to evaluate experimentally,
especially with physiological ion concentrations which are typically quite low.

@@

@@

\todo{SAMULI: Controversies in previous simulations (https://doi.org/10.1016/j.bpj.2018.08.044 and
  Melcrova et al. Scientific Reports | 6:38035 | DOI: 10.1038/srep38035) should be mentioned also
in the intro.}

>>>>

Lipids with negatively charged headgroups, like phophatidylserine
play important role in biomembranes. 
Signaling molecules in cells interact with lipid membranes 
due to specific, often electrostatically driven, interactions 
with anionic lipids \cite{lemmon08,leventis10}.
Anionic lipids and their interactions with ions play also role in membrane
fusion \cite{??}. \todo{Pavel can probably improve this and give a citation}
These interactions depend both on
the chemical details of lipid headgroups as well as 
on the binding of counter and co-ions to anionic membranes.

Various interaction schemes have been proposed for the negatively charged
lipids with ions and other lipids. 
Some studies suggest that the
binding constant of ions to negatively charged lipids is similar to that of zwitterionic lipids,
and the binding affinity is increased only due to the increased cation
concentration in the vicinity of the membrane \cite{seelig90,sinn06}.
On the other hand, calcium forms dehydrated complexes with PS headgroups
which cause phase separation \cite{hauser77,kurland79,hauser85,feigenson86,mattai89,roux90,roux91,boettcher11}.
Different theories are difficult to evaluate experimentally,
especially with physiological ion concentrations which are typically quite low.

@@

Short paragraph describing previous MD-work on this topic (PS), i.e., \dots 
\todo{SAMULI: Controversies in previous simulations (https://doi.org/10.1016/j.bpj.2018.08.044 and
  Melcrova et al. Scientific Reports | 6:38035 | DOI: 10.1038/srep38035) should be mentioned also
in the intro.}

@@
